---
title: "scMCA package manual"
author: "Yincong Zhou"
package: scMCA
date: "`r Sys.Date()`"
output: BiocStyle::html_document2
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction

single-cell MCA analysis(`scMCA`) is a tool for defining cell types in mouse based on single-cell digital expression. scMCA maps scRNA-seq data to previously built Mouse Cell Atlas(`MCA`) reference and returns correlation of query singe cell and reference matrix. scMCA also provides a interactive GUI to visualize the returned results.

# Quick Start

## data input
Currently, a dataframe or matrix whcih contains expression data can be directly put into scMCA. An example expression matrix from MCA is embeded in scMCA. The dataset(`mca_lung`)   

```{r, message=FALSE, warning=FALSE}
library(scMCA)

knitr::kable(mca_lung$data[1:10,1:5])
dim(mca_lung$data)
```

# GUI method

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
pheatmap::pheatmap(mca_lung$data)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

# Detail

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
